---
title: "Explanatory and Regression"
author: "Yanyue Fu, Rui Xu"
date: "12/12/2019"
output: pdf_document
---
```{r results='hide', message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(lfe)
library(cluster)
library(factoextra)
cbd = read_csv("cbd-cleaned.csv")
```

**Variable explanation**

`id`: The participant's id.
`before`: Participant's reaction time before experiment.
`after`: Participant's reaction time after experiment.
`AGE`: Participant's age.
`gender (1/0)`: Participant's gender, 1 is for male and 0 is for female.
`diff`: The difference in reaction time between pre-experiment and post-experiment (`before` - `after`).

**EDA**

To get a better understanding of our cbd and gain some insight through exploring cbd, we did the Exploratory cbd analysis. Figure 1 shows the distribution of reaction test time before and after the experiment, categorized by gender and treatment/placebo group. For female before taking the experiment, the reaction time in the placebo group are relatively more concentrated and lower than the female observations in the treatment group. After the experiment, both two female groups’ performances were increased and the reaction time was dropped. But the time declined larger for females in the placebo group than treatment group. 


For males before the experiment, the reaction time for placebo group is relatively higher than treatment group. After the experiment, the reaction time for both groups was decreased but the placebo group decreased slightly more than the treatment group. The result implied the effect of CBD oil actually is unobvious since there is not a high-increased performance for the treatment group when compared to the control group. 

```{r echo=FALSE}
cbd %>%
  mutate(treatment = ifelse(treatment == 'A', 0, 1)) %>%
  select(id, gender = `gender (1/0)`, everything())-> cbd1
names(cbd1) = str_to_lower(names(cbd1))
cbd1 %>% 
  gather(., "before", "after", key = "time", value = "reflection_time") %>%
  mutate(gender = ifelse(gender == 0, "female", "male")) %>%
  mutate(treatment = ifelse(treatment == 0, "placebo", "treatment")) -> cbd2
ggplot(cbd2, aes(x = factor(gender), y = reflection_time, fill = time)) +
  geom_boxplot() + 
  facet_grid(~treatment) +
  labs(x = 'gender', y = "refection time", 
       title = "Figure1: The distribution in reaction time based on gender and experiment")
```

Figure 2 is a more concretely inspection from Figure 1, showing the difference in reaction time based on gender. All of the `difference` are above 0, means that participants will have shorter reaction time after experiment. The reduced reaction time can be explained by the manipulation in the second reaction testing. Compared with placebo group, the treatment group has less difference which indicats that the reaction time reduced less after using the CBD. There is more difference between placebo group and experiment group for female than male, which reveals that female are more easily affected by the CBD.

```{r echo=FALSE}
cbd %>% ggplot(aes(x= factor(`gender (1/0)`), y = diff, fill = treatment))+
  geom_boxplot() +
  labs(
       title = "Figure2: The difference in reaction time based on gender",
       y = "difference",
       x = "female                                             male")
```

Figure 3 shows the average difference For Each Age Bin. Since the interval of participants' age is 21 to 35 in our experiment, we decided to separte them into 3 age bins for analysis. Age Bin By 5 (1 = 20-25, 2 = 25-30, 3 = 30-35). CBD has the greatest impact on the people among 25 to 30 years old and has least impact on people among 20 to 25 years old.

```{r echo=FALSE}
cbd$ageRange <- findInterval(cbd$AGE, c(20, 25, 30, 35))
cbd %>% 
  group_by(ageRange,treatment) %>% 
  summarize(totaldiff=mean(diff)) %>% 
  ggplot(aes(x= as.factor(ageRange), y=totaldiff,fill = treatment)) +
  geom_col(position = "dodge") +
  labs(title = "Figure3: Average difference For Each Age Bin", 
       x = "Age Bin By 5 (1 = 20-25, 2 = 25-30, 3 = 30-35)",
       y = "Average difference of reaction time", 
       fill = "Treatment") 
```

## Regression
# Regression with fixed effect
In order to measure the effects of the treatment precisely, we can put in age and gender fixed effects. We decided to apply three different fixed effects: only age, only gender and both of them. Given that regressions allow us to compute standard errors, we observed that the standard error has declined when we applied `gender` as fixed effect. However, the variable `treatment` is not statistically significant so we cannot reject the null hypothesis.
```{r echo=FALSE, message=FALSE, warning=FALSE}
treat1 = felm(diff ~ treatment, data = cbd1)
treat2 = felm(diff ~ treatment | age, data = cbd1)
treat3 = felm(diff ~ treatment | gender, data = cbd1)
treat4 = felm(diff ~ treatment | age + gender, data = cbd1)
stargazer(treat1, treat2, treat3, treat4, type = "text")
```

## regression about co-variance

We use fixed linear regression to inspect the covariance between the treatment and other interactive variables. Since the performance for reaction test is varied over personal physical factors, we collected the gender and age inform from participants as two interactive variables which also would affect the reaction test outcome.  We try to inspect whether there exists significantly covariance between the treatment and the variable gender and age. And for a more reliable regression outcome, we take one interactive variable as a fixed effect when we test the other interactive variable. 
There are the two regression, and the result is showed at the following table;
            **difference = treatment + gender + treatment*gender**
            **difference = treatment + age + treatment*age**
            
The result indicated that in both two regression models, the effect of CBD oil on difference in reaction time is not significant with the interacted effect from gender and age. And both the covariance of treatment to gender and the covariance of treatment to age are not significant. We cannot reject the hypothesis that there doesn’t exist any covariance between both CBD treatment to gender and CBD treatment to age. In summary, we conclued that the CBD has no effect on people's reaction time. 

```{r echo=FALSE, warning=FALSE, massage=FALSE}
treat_n_gender = felm(diff ~ treatment * gender | age, data = cbd1)
treat_n_age = felm(diff ~ treatment * age | gender, data = cbd1)
stargazer(treat_n_gender, treat_n_age, type = "text")
```

## Limitation We Got
There are several limitations in our study. We tried our best to run the experiment, however, our study had several limitations. Below are the five main limitations: 
1. The first challenge we met was the sample size of the experiment. Because CBD oil is a new product, it is hard to find people willing to participate in the experiment. The total sample we got is only 40 which didn’t meet size of experiment size that designed.
2. During the experiment, some of the experimentees see what treatment they’ve assigned. Thus it is possible this affects their behavior. Our experiment is not double blind. 
3. The experiment is not fully meet exclubitility. Because some people know not only what they took, they also knew what other people took. Thus they communicated. Part of the treatment group was affected by the placebo group. 
4. Most people who attend the experiment is among 21-25. There is a limitation on the age range. The result of the experiment can’t explain all people’s behaviro who are not within the age range.
5. Over 90% of people get a higher score after the assign the treatment or placebo, and some people have a big improvement after playing the first round. We concern may be the warm-up exercise is not enough for people to get familiar with the experiment. We should set more warm-up exercise to people so that can reduce the bias from the familiarity of the game. 







